Hybrid platforms and bargaining power

### 2023-02-03 src/paper/application.tex
Start working on more general model

\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}

@@

>>>>

\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}

@@

\section{Model}

This section introduces the model used throughout the paper.
I use the terms ``platform'' and ``fringe sellers'', and present my ideas in the context of an intermediated market, such as an online marketplace or an application store.
However, the model is more general, and the results apply to a broader class of settings.
Chief among these is an upstream-downstream setting, with a single upstream producer and a continuum of downstream sellers.

I make use of a reduced-form, but quite general approach to model production and demand.
Assume that the total profits obtained by the platform and the fringe sellers are described by the function $f(n_P, n_F)$.
Here, $n_F$ is the mass of fringe sellers, and $n_P$ measures the degree to which the platform sells its own products.
In case the platform operates as a pure intermediary, $n_P = 0$.
For example, in a setting with differentiated products and monopolistic competition, $n_F$ and $n_P$ represents the product variety of the fringe and the platform, respectively.

I will assume that total profits are increasing in both arguments.
\begin{assumption}
    \label{ass:monotone_profits}
    $f(n_P, n_F)$ is increasing in both $n_P$ and $n_F$.
\end{assumption}
Such profit functions arise in a variety of settings in which the profit reduction from increased competition is dominated by extra sales due to increased variety.
One such example is \textcite{anderson2020aggregative}, where the demand exhibits love for variety, while consumers have access to an outside option.
Alternatively, indirect network effects, such as in two-sided markets, can also result in such profit functions.

\subsection{Profit sharing}

Let us assume that the fringe firms are unable to sell their products directly to consumers.
Instead, they must sell through the platform.
For this service, the platform may charge a fee, and obtain a share of the fringe's profits.

Let us assume that the platform and the fringe shares their total profits according to the following rule.
\begin{assumption}
    \label{ass:profit_sharing}
    Let $w: [0, 1] \to \mathbb{R}^+$ such that $\int_0^1 w(s) \ds = 1$. 
    \begin{align*}
        \pi_P(N_P, N_F) &= \int_0^1 w(s) f(N_P, s N_F) \ds, \\
        \pi_F(N_P, N_F) &= f(N_P, N_F) - \int_0^1 w(s) f(N_P, s N_F) \ds.
    \end{align*}
\end{assumption}

While at first it might seem rather arbitrary, and much more convoluted than a simple percentage split, it has quite a few nice properties compared to the latter, and can also be microfounded.

\subsection{Entry}

\subsection{Equilibrium}

\begin{assumption}
    \label{ass:single_crossing}
    Let $f(n_P, n_F)$ and $w(s)$ be such that the following holds for all $N_F, N_P \geq 0$:
    \begin{gather*}
        f'_{n_F} (N_P, N_F) < \int_0^1 s w(s) f'_{n_F} (N_P, s N_F) \ds \\
        \text{or} \\
        f''_{n_F} (N_P, N_F) < \int_0^1 s^2 w(s) f''_{n_F} (N_P, s N_F) \ds.
    \end{gather*}
\end{assumption}
